Molecular Gas Kinematics of the Strongly-Lensed Quasar Host Galaxy RXS J1131$-$1231

### 2016-11-23 WRITEUP/table_magFactor.tex
swapped mag. for RXJ1131 and companion. if showing spectrum, where companion has lower intrinsic flux, then it must have higher mag. factor; CAVEAT: didn't recalc. the weighted average in magnnification factor, but should be fine because we only use the median and not the weighted average in physical parameters"

\begin{deluxetable}{lcc}[!htbp]
\tabletypesize{\scriptsize}
\tablecolumns{3}
\tablecaption{Magnification factors of various kinematic components in \bco}
\tablehead{
\colhead{Velocity Range (\kms)} & % see 02July16/velo_res_obs.txt (2nd column), which corresponds to rest-frame velocity at z=0.6541, taken from the central of each bin
\colhead{Source 1 $\mu_{\rm L}$} &
\colhead{Source 2 $\mu_{\rm L}$}
}
\startdata
346\,$-$\,260       & 7.2 $\pm$ 5.6 & 6.7 $\pm$ 2.5 \\ 
238\,$-$\,153       & 7.6 $\pm$ 1.6 & \\ [0.7ex]\hline
131\,$-$\,45        & 8.7 $\pm$ 2.0 & \\ [0.5ex]
24\,$-$\,-62    & 4.1 $\pm$ 0.9 & \\ [0.5ex]
-84,$-$\,-170  & 4.2 $\pm$ 0.6 & \\ [0.5ex]
-191\,$-$\,-277 & 4.3 $\pm$ 2.4 & \\ [0.5ex]
-300\,$-$\,-385 & 3.1 $\pm$ 0.9 & \\ [0.5ex]
weighted average & 4.4 & \rule{0pt}{1\normalbaselineskip}\\ [0.5ex]
median & 5.5 &
\enddata
\label{tab:model}
\tablecomments{First column corresponds to the rest-frame velocity ranges taken from the center of an unbinned channel
(see \Fig{delensed}). Each row corresponds to a (binned) channel slice used for
lens modeling. Source 1 is RXJ1131 and source 2 is its companion. }
\end{deluxetable}

>>>>

\begin{deluxetable}{lcc}[!htbp]
\tabletypesize{\scriptsize}
\tablecolumns{3}
\tablecaption{Magnification factors of various kinematic components in \bco}
\tablehead{
\colhead{Velocity Range (\kms)} & % see 02July16/velo_res_obs.txt (2nd column), which corresponds to rest-frame velocity at z=0.6541, taken from the central of each bin
\colhead{Source 1 $\mu_{\rm L}$} &
\colhead{Source 2 $\mu_{\rm L}$}
}
\startdata
346\,$-$\,260       & 6.7 $\pm$ 2.5 &  7.2 $\pm$ 5.6 \\
238\,$-$\,153       & 7.6 $\pm$ 1.6 & \\ [0.5ex]
131\,$-$\,45        & 8.7 $\pm$ 2.0 & \\ [0.5ex]
24\,$-$\,-62    & 4.1 $\pm$ 0.9 & \\ [0.5ex]
-84\,$-$\,-170  & 4.2 $\pm$ 0.6 & \\ [0.5ex]
-191\,$-$\,-277 & 4.3 $\pm$ 2.4 & \\ [0.5ex]
-300\,$-$\,-385 & 3.1 $\pm$ 0.9 & \\ [0.7ex]\hline
weighted average & 4.4 & \rule{0pt}{1\normalbaselineskip}\\ [0.5ex]
median & 5.5 &
\enddata
\label{tab:model}
\tablecomments{First column corresponds to the rest-frame velocity ranges taken from the center of an unbinned channel
(see \Fig{delensed}). Each row corresponds to a (binned) channel slice used for
lens modeling. Source 1 is RXJ1131 and source 2 is its companion. }
\end{deluxetable}
